A Detection of the Environmental Dependence of the Stellar Profiles and Halos of Massive Central Galaxies

### 2017-07-12 draft/paper2.tex
Data and sample: edit 3
Edit results 1

@@

    Massive central galaxies in this work show an intriguing diversity on the plane 
    defined by these two metrics.  
    We preview this using Fig~\ref{fig:m100_m10_color}, which shows a subsample of 
    massive galaxies at $z{\sim} 0.4$ that share very similar value of \minn{}, but 
    exhibit a large diversity in their outer profiles. 
    Assuming that galaxies at fixed \minn{} share a similar in-situ formation history, 
    it is of great interest to investigate the relation between their present day halo 
    mass and the extend of their outer envelopes. 
    We note that although a circular aperture is shown on Fig~\ref{fig:m100_m10_color}, 
    for our mass measurements, we always use elliptical apertures that follow the 
    average isophotal shape. Finally, given our narrow mass and redshift range, we 
    can safely ignore significant mass growth and structural evolution in this work
    (no star formation, lower merger rate \etal~e.g.\ \citealt{Bellstedt2016},
    \citealt{Inagaki2015}; but also see \citealt{Bai2014}).

@@

%% ------------------------------------------------------------------------------------ %% 
\section{A. Basic Statistical Properties of the Sample} 
	\label{app:sedasic}

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=16.5cm]{fig/redbcg_sample_stats}
      \caption{
          \textbf{Top-left}: The \logms{}-$g-r$ color relation of the \rbcg{} 
          (red circle; detaield format is the same with the right panel of 
          Fig~\ref{fig:smf1}) and \nbcg{} (grey dots) samples.
          We apply the $k$-corrections from \texttt{iSEDFit} fitting to the colors.~~          
          \textbf{Top-right}: the histograms of the redshift for the \rbcg{} and 
          \nbcg{} galaxies in both \logmtot$>11.2$ and $11.6<$\logmtot{}$<11.9$
          mass bins.
          The vertical lines highlights the $0.3\leq z \leq 0.5$ redshift range.~~
          \textbf{Bottom-left}: the histograms of \mtot{} for the \rbcg{} (orange-red) 
          and \nbcg{} (grey-black) samples at both $z>0.2$ (step-filled histogram) and 
          $0.3 \leq z \leq 0.5$ (stepped histogram). 
          The vertical lines in both top-left and bottom-left figures highlight the 
          $11.6<$\logmtot{}$<11.9$ mass range that will be used in the comparison of 
          the \mtot{}-matched samples.~~
          \textbf{Bottom-right}: the histograms of \minn{} in similar format. 
          Here the vertical lines highlight the 
          $11.2<$\logminn{}$<11.6$ mass range that is used for comparison.
      }
      \label{fig:sample_stats}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

>>>>

    In Appendix~\ref{app:basic}, we show the distributions of redshift, \mtot{}, and 
    \minn{} for \rbcg{} and \nbcg{} samples. 
    We also compare these two samples on the \mtot{} - rest-frame $g-r$ color plane. 
    Both of them follow the same ``red-sequence'' without much contamination from the 
    ``blue clouds''.

@@

    As shown in Figure~\ref{fig:m100_m10_color}, massive central galaxies show 
    intriguing diversity on the \mtot{}-\minn{} plane and in their \mden{} profiles 
    in the outer haloes.  
    In Paper~1, we explore the \mstar{}-dependence of the stellar halos in massive 
    galaxies, and conclude that the general trends are consistent with the 
    predictions of two-phase formation scenario. 
    In the following sections, we will investigate the relation between their 
    present day halo mass and their stellar haloes using the \mden{} profiles and 
    scaling relations for massive central galaxies with different $M_{\mathrm{200b}}$ 
    (\rbcg{} and \nbcg{}).

    We should emphasize again that although a circular aperture is shown on 
    Fig~\ref{fig:m100_m10_color}, we extract 1-D \mden{} profiles, estimate 
    \mtot{} and \minn{} using elliptical apertures defined by fluxed-weighted average 
    isophotal shape. 
    And, given the narrow \mstar{} and redshift range, we ignore \mstar{} growth 
    and structural evolution here
    (no star formation, lower merger rate \etal~e.g.\ \citealt{Bellstedt2016},
    \citealt{Inagaki2015}; but also see \citealt{Bai2014}).

@@

%% ------------------------------------------------------------------------------------ %% 
\section{A. Basic Statistical Properties of the Sample} 
	\label{app:basic}

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=16.5cm]{fig/redbcg_sample_stats_old}
      \caption{
          \textbf{Top-left}: The \logms{}-$g-r$ color relation of the \rbcg{} 
          (red circle; detaield format is the same with the right panel of 
          Fig~\ref{fig:smf1}) and \nbcg{} (grey dots) samples.
          We apply the $k$-corrections from \texttt{iSEDFit} fitting to the colors.~~          
          \textbf{Top-right}: the histograms of the redshift for the \rbcg{} and 
          \nbcg{} galaxies in both \logmtot$>11.2$ and $11.6<$\logmtot{}$<11.9$
          mass bins.
          The vertical lines highlights the $0.3\leq z \leq 0.5$ redshift range.~~
          \textbf{Bottom-left}: the histograms of \mtot{} for the \rbcg{} (orange-red) 
          and \nbcg{} (grey-black) samples at both $z>0.2$ (step-filled histogram) and 
          $0.3 \leq z \leq 0.5$ (stepped histogram). 
          The vertical lines in both top-left and bottom-left figures highlight the 
          $11.6<$\logmtot{}$<11.9$ mass range that will be used in the comparison of 
          the \mtot{}-matched samples.~~
          \textbf{Bottom-right}: the histograms of \minn{} in similar format. 
          Here the vertical lines highlight the 
          $11.2<$\logminn{}$<11.6$ mass range that is used for comparison.
      }
      \label{fig:sample_stats}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%
